Comparison of FDR methods on GWAS with SummarizedBenchmark

### 2018-02-15 datasets/GWAS/GWAS-SummarizedBenchmark.Rmd
Use download.file instead of bash calls to fetch data

---
title: "Comparison of FDR methods on GWAS with SummarizedBenchmark"
author: "Keegan Korthauer"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/n/irizarryfs01_backed_up/kkorthauer/FDR")
```

@@

```{r, wkspace-setup, results='hide', message=FALSE, warning=FALSE}
# project directory & data/results folders - the datdir needs to match where
#  files are downloaded with the first few bash chunks
#setwd("/n/irizarryfs01_backed_up/kkorthauer/FDR")
datdir <- "DATA/GWAS/"
resdir <- "RESULTS/GWAS/"

@@

# comparison tools/functions
library(SummarizedBenchmark)
sourceDirectory("benchmark-fdr/datasets/R/")

@@

```{bash, GWAS1-download, eval=FALSE}
curl -o DATA/GWAS "http://portals.broadinstitute.org/collaboration/giant/images/3/3a/BMI.SNPadjSMK.zip"
```

@@

```{bash, GWAS1-unzip, eval=FALSE}
unzip DATA/GWAS/BMI.SNPadjSMK.zip
rm DATA/GWAS/BMI.SNPadjSMK.zip
rm DATA/GWAS/BMI.SNPadjSMK.Women.EuropeanOnly.txt
rm DATA/GWAS/BMI.SNPadjSMK.Women.AllAncestry.txt
rm DATA/GWAS/BMI.SNPadjSMK.Men.EuropeanOnly.txt
rm DATA/GWAS/BMI.SNPadjSMK.Men.AllAncestry.txt
rm DATA/GWAS/BMI.SNPadjSMK.CombinedSexes.AllAncestry.txt
```

@@

```{bash, GWAS1-refdata, eval=FALSE}
# download CEU 1000 genomes SNP reference data 
wget 'http://neurogenetics.qimrberghofer.edu.au/iSECA/1000G_20101123_v3_GIANT_chr1_23_minimacnamesifnotRS_CEU_MAF0.01.zip' -P DATA/GWAS/

# unzip reference data
unzip DATA/GWAS/1000G_20101123_v3_GIANT_chr1_23_minimacnamesifnotRS_CEU_MAF0.01.zip -d DATA/GWAS
```

@@

And we'll clean up the workspace before moving on to the next dataset.

>>>>

---
title: "Comparison of FDR methods on GWAS with SummarizedBenchmark"
author: "Keegan Korthauer"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
    html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r, wkspace-setup, results='hide', message=FALSE, warning=FALSE}
system("mkdir -p DATA")
system("mkdir -p RESULTS")
datdir <- "DATA/"
resdir <- "RESULTS/"

@@

# comparison tools/functions
library(SummarizedBenchmark)
sourceDirectory("../R/")

@@

```{r, GWAS1-download}
download.file(url="http://portals.broadinstitute.org/collaboration/giant/images/3/3a/BMI.SNPadjSMK.zip", 
             destfile=paste0(datdir,"BMI.SNPadjSMK.zip")) 
```

@@

```{r, GWAS1-unzip}
system(paste0("unzip ", datdir, "BMI.SNPadjSMK.zip"))
system(paste0("rm ", "BMI.SNPadjSMK.Women.EuropeanOnly.txt"))
system(paste0("rm ", "BMI.SNPadjSMK.Women.AllAncestry.txt"))
system(paste0("rm ", "BMI.SNPadjSMK.Men.EuropeanOnly.txt"))
system(paste0("rm ", "BMI.SNPadjSMK.Men.AllAncestry.txt"))
system(paste0("rm ", "BMI.SNPadjSMK.CombinedSexes.AllAncestry.txt"))
system(paste0("mv BMI.SNPadjSMK.CombinedSexes.EuropeanOnly.txt ", datdir))
system(paste0("rm -f ", datdir, "/*.zip"))
```

@@

```{r, GWAS1-refdata}
# remove remnants of previous runs, if present
system(paste0("rm -f ", datdir, "/*CEU_MAF0.01*"))

# download CEU 1000 genomes SNP reference data 
download.file(url="http://neurogenetics.qimrberghofer.edu.au/iSECA/1000G_20101123_v3_GIANT_chr1_23_minimacnamesifnotRS_CEU_MAF0.01.zip", 
              destfile=paste0(datdir, "1000G_20101123_v3_GIANT_chr1_23_minimacnamesifnotRS_CEU_MAF0.01.zip"))

# unzip reference data
system(paste0("unzip ", datdir, "1000G_20101123_v3_GIANT_chr1_23_minimacnamesifnotRS_CEU_MAF0.01.zip -d ", datdir))
system(paste0("rm ", datdir, "1000G_20101123_v3_GIANT_chr1_23_minimacnamesifnotRS_CEU_MAF0.01.zip"))
```

@@

Clean up the workspace.
